Untitled

### 2018-08-17 MSOAmodel.Rmd
Cleaning and don't ruin postocdes

MSOAtoLAD %>%
  group_by(LAD11CD) %>%
  summarise(counts = n(),
            LAD11NM = first(LAD11NM)) %>%
  pull(counts) %>% mean

@@

@@

These models work at MSOA level only and include data from the LAD level
Tehy are rubbish so aren't included in the main work. Just kept here so I don't forget I have already checked.

DATAdf %>%
  arrange(LAD11NM) %>% pull(LAD11NM) %>% unique

MSOAMean2 <-MSOAMean %>%
  mutate(RelativeAfford = AffordRatio/LADAffordRatio,
         RelativeTourismDens = TourismDensity/LADTourismDensity,
         RelativeTourismDens = ifelse(is.finite(RelativeTourismDens), RelativeTourismDens, 100)) %>%
  filter(!is.na(HighVal)) #Temporary  until I work out how to get rid of those weird MSOA

KitchenSink <- as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2+ RelativeAfford +RelativeTourismDens+
                            LADTourismDensity+ LADAffordRatio+ LADAffordRatio2)

KitchenSink2 <- as.formula(Reference ~RelativeAfford +RelativeTourismDens+
                            LADTourismDensity+ LADAffordRatio)
Formulas2 <- c(as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2),
               KitchenSink)

set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean2 , c(test = 0.2, train = 0.8)))

MSOAModels2 <-LinearClassifierCombiner(MSOAMean2,  Outcomes, Formulas2, TestResample) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           LAD = grepl("LAD", Formula)
         )

@@

library(ranger)

#Just under 78% better than all other models
ResOut <- MSOAMean2 %>%
  mutate(Reference = HighLUP) %>% 
  TreeResampledModelPerf(., TestResample, KitchenSink)

ResOut2 <- MSOAMean2 %>%
  mutate(Reference = HighLUP) %>%
  TreeResampledModelPerf(., TestResample, KitchenSink2)

ResOut %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

ResOut2 %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

@@

```{r}
#This model uses information from the over all LUP as a result I need to subset the data by lups then train on the MSOA
set.seed(1983)
TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))

ComplexModels <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      TreeResampledModelPerf(., TestResample, KitchenSink, CombineData = TRUE) %>%
      mutate(Dependent = .x)
})

@@

ComplexModels2 <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      TreeResampledModelPerf(., TestResample, KitchenSink2, CombineData = TRUE) %>%
      mutate(Dependent = .x)
})

@@

Modeldf <-MSOAMean2 %>%
      rename_(Reference = "LADHighLUP")

@@

@@

test <- MSOAMean2 %>%
      rename_(Reference = "LADHighLUP") %>%
MSOATreeVoting(., TestResample, KitchenSink )

test %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )

>>>>

@@

MSOAEgoList1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
names(MSOAEgoList1) <- get.vertex.attribute(MSOAgraph, "name")

MSOAEgoList2 <- ego(MSOAgraph, 2) %>%map(~names(.x))
names(MSOAEgoList2) <- get.vertex.attribute(MSOAgraph, "name")

 TourismMSOAEgo2 <- MSOAEgoList %>% map_dbl(~{
   print(.x)
    Tourism %>%
      filter(MSOA11CD %in% .x) %>%
      pull(Tourism) %>% sum
 }) %>%
   tibble(Ego2Tourism = .,
          MSOA = names(MSOAEgoList))

  TourismMSOAEgo1 <- MSOAEgoList1 %>% map_dbl(~{
   print(.x)
    Tourism %>%
      filter(MSOA11CD %in% .x) %>%
      pull(Tourism) %>% sum
 }) %>%
   tibble(Ego1Tourism = .,
          MSOA = names(MSOAEgoList1))

@@

These models work at MSOA level only and include data from the LAD level
They don't really add anything extra so aren't included in the main work. Just kept here so I don't forget I have already checked.

```{r}
MSOAMean2 <-MSOAMean %>%
  mutate(RelativeAfford = AffordRatio/LADAffordRatio,
         RelativeTourismDens = TourismDensity/LADTourismDensity,
         RelativeTourismDens = ifelse(is.finite(RelativeTourismDens), RelativeTourismDens, 100),
         HighFinance = factor("TRUE"==LADHighVal & "TRUE"==HighLUP, levels = c("TRUE", "FALSE"))) %>%
  filter(!is.na(HighVal)) #Temporary  until I work out how to get rid of those weird MSOA

KitchenSink <- as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2+ RelativeAfford +RelativeTourismDens+
                            LADTourismDensity+ LADAffordRatio+ LADAffordRatio2+ LADMeanMedianRatio)

KitchenSink2 <- as.formula(Reference ~RelativeAfford + RelativeTourismDens +
                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio)

Formulas2 <- c(as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2),
               KitchenSink)

####Needs updating
MSOAModels2 <-LinearClassifierCombiner(MSOAMean2,  Outcomes, Formulas2, TestResample) %>%
  mutate(IncAfford2 = grepl("2", Formula),
           LAD = grepl("LAD", Formula)
         )

@@

#Just under 76%. Better than all other models...but is it?
#The more LAD variables that are included the better the model gets... Until you find out that this is becuase the model uses the lad data to predict the results of other MSOA in the same lad.
ResOut <- MSOAMean2 %>%
  mutate(Reference = HighLUP) %>% 
  TreeResampledModelPerf(., MSOAHighLUPResample, KitchenSink2)

#Data contains LAD information I account for that here

ResOut2 <- MSOAMean2 %>%
  mutate(Reference = HighLUP) %>%
  TreeResampledModelPerf(., LADHighLUPResample, KitchenSink2, LADData = LADMean )

#The model was getting information from the shared LAD data so making it appear much better than it really is
ResOut %>% SummariseModels()
ResOut2 %>% SummariseModels()

@@

```{r}
#This model uses information from the over all LUP as a result I need to subset the data by lups then train on the MSOA
set.seed(1983)
TestResample <- vfold_cv(LADMean, v = 5, repeats = 20)

ComplexModels <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean) %>%
      mutate(Dependent = .x)
})

#the data from the Lup is increasing the accuracy of the model
ResOut2 <- MSOAMean2 %>%
  mutate(Reference = HighLUP) %>%
  TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean)

@@

ComplexModels2 <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean) %>%
      mutate(Dependent = .x)
})

@@

@@

Highly financialized

```{r}
KitchenSink2 <- as.formula(Reference ~RelativeAfford + RelativeTourismDens +
                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio, Ego2TourismDens2+Ego2TourismDens)

test <- MSOAMean2 %>%
  select(HighFinance, LADHighVal, HighLUP)

ComplexModels2 <- c("HighFinance", "HighLUP", "LADHighVal") %>%
  map_df(~{
    print(.x)
    ResOut2 <- MSOAMean2 %>%
      rename_(Reference = .x) %>%
      TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean) %>%
      mutate(Dependent = .x)
})

ComplexModels2 %>%
  group_by(Dependent) %>%
  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
            Accuracy = mean(Accuracy), #What was the mean accuracy
            'NULL Model' = mean(AccuracyNull),
           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
            )
```

@@

test <- MSOAMean2 %>% left_join(MSOAtoLAD) %>%
      rename_(Reference = "LADHighLUP") %>%
MSOATreeVoting(., TestResample, KitchenSink2 )

test %>% SummariseModels()
